Course Project 2
==============================================================

## 1. Title : The TORNADO is the climatic biggest problem in US 

## 2. Synopsis
  Severe weather events may cause serious public health & economic burdens for communities. According to the U.S. National Oceanic and Atmospheric Administrations(NOAA) storm database, the weather conditions were categorized as 48 events. Among them, the TONADO is the biggest problem as a concern of both health and economy. The TONADO caused total 84.742 causualities (4,658 fatalities and 80084 injuries) and 41 billions damages.(Most of damages caused by TONADO was products. The most considerable crop damage was induced by DROUGHT.)
  
 
## 3. Data Processing
```{r read_preprocessing_data, echo=TRUE}
workingpath <- "C:\\Users\\MED1\\ReprodRes"
setwd(workingpath)

##### read & preprocess data #####
download.file ("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2", "stormdata.csv.bz2")
storm <- read.csv("stormdata.csv.bz2", header=TRUE)

# types of events #
event <- c("ASTRONOMICAL LOW TIDE", "AVALANCHE", "BLIZZARD", "COASTAL FLOOD", "COLD/WIND CHILL",
           "DEBRIS FLOW", "DENSE FOG", "DENSE SMOKE", "DROUGHT", "DUST DEVIL",
		   "DUST STORM", "EXCESSIVE HEAT", "EXTREME COLD/WIND CHILL", "FLASH FLOOD", "FLOOD",
		   "FROST/FREEZE", "FUNNEL CLOUD", "FREEZING FOG", "HAIL", "HEAT",
		   "HEAVY RAIN", "HEAVY SNOW", "HIGH SURF", "HIGH WIND", "HURRICANE",
		   "ICE STORM", "LAKE-EFFECT SNOW", "LAKESHORE FLOOD", "LIGHTNING", "MARINE HAIL",
		   "MARINE HIGH WIND", "MARINE STRONG WIND", "MARINE THUNDERSTORM WIND", "RIP CURRENT", "SEICHE",
		   "SLEET", "STORM SURGE/TIDE", "STRONG WIND", "THUNDERSTORM WIND", "TORNADO",
		   "TROPICAL DEPRESSION", "TROPICAL STORM", "TSUNAMI", "VOLCANIC ASH", "WATERSPOUT",
		   "WILDFIRE", "WINTER STORM", "WINTER WEATHER")

name.select <- c("EVTYPE", "FATALITIES", "INJURIES", "PROPDMG", "PROPDMGEXP", "CROPDMG", "CROPDMGEXP")
storm.sub <- subset(storm, select=name.select)
rm(storm)

# select cases according to events #
n.event <- length(event)
event.id <- vector()
for (i in c(1:n.event)){
	event.id <- c(event.id, which(storm.sub$EVTYPE==event[i]))
}
storm.sub <- storm.sub[event.id,]

# change types of variables #
as.numeric.factor <- function (x) { as.numeric(levels(x))[x] }
storm.sub$FATALITIES <- as.numeric.factor(storm.sub$FATALITIES)
storm.sub$INJURIES <- as.numeric.factor(storm.sub$INJURIES)
storm.sub$PROPDMG <- as.numeric.factor(storm.sub$PROPDMG)
storm.sub$CROPDMG <- as.numeric.factor(storm.sub$CROPDMG)

storm.sub$EVTYPE <- as.character(storm.sub$EVTYPE)
storm.sub$PROPDMGEXP <- as.character(storm.sub$PROPDMGEXP)
storm.sub$CROPDMGEXP <- as.character(storm.sub$CROPDMGEXP)

# calculate the amounts of damage #
PROPDMG.K.index <- which(storm.sub$PROPDMGEXP == "K")
PROPDMG.M.index <- which(storm.sub$PROPDMGEXP == "M")
PROPDMG.B.index <- which(storm.sub$PROPDMGEXP == "B")
CROPDMG.K.index <- which(storm.sub$CROPDMGEXP == "K")
CROPDMG.M.index <- which(storm.sub$CROPDMGEXP == "M")
CROPDMG.B.index <- which(storm.sub$CROPDMGEXP == "B")

storm.sub$PROPDMG[PROPDMG.K.index] <- storm.sub$PROPDMG[PROPDMG.K.index] * 10^3
storm.sub$PROPDMG[PROPDMG.M.index] <- storm.sub$PROPDMG[PROPDMG.M.index] * 10^6
storm.sub$PROPDMG[PROPDMG.B.index] <- storm.sub$PROPDMG[PROPDMG.B.index] * 10^9
storm.sub$CROPDMG[CROPDMG.K.index] <- storm.sub$CROPDMG[CROPDMG.K.index] * 10^3
storm.sub$CROPDMG[CROPDMG.M.index] <- storm.sub$CROPDMG[CROPDMG.M.index] * 10^6
storm.sub$CROPDMG[CROPDMG.B.index] <- storm.sub$CROPDMG[CROPDMG.B.index] * 10^9

# total amount of health problems & economic problems #
storm.sub$HEALTHPOP <- storm.sub$FATALITIES + storm.sub$INJURIES
storm.sub$DMGTOTAL <- storm.sub$PROPDMG + storm.sub$CROPDMG
```

## 4. Results
```{r total_damages, echo=TRUE}
##### Data analysis #####
# total amount of damages - population health & economic consequences #
library(dplyr)
storm.evtype <- group_by(storm.sub, EVTYPE)
storm.evtype.healthpop.sum <- summarise(storm.evtype, sum.health = sum(HEALTHPOP, na.rm=TRUE))
storm.evtype.dmgtotal.sum <- summarise(storm.evtype, sum.dmg = sum(DMGTOTAL, na.rm=TRUE))

storm.evtype.healthpop.sum$EVTYPE[which(storm.evtype.healthpop.sum$sum.health == max(storm.evtype.healthpop.sum$sum.health))]
storm.evtype.dmgtotal.sum$EVTYPE[which(storm.evtype.dmgtotal.sum$sum.dmg == max(storm.evtype.dmgtotal.sum$sum.dmg))]
```

```{r fig.cap = "total health & economic problems"}
par(mfrow=c(1, 2))
barplot(storm.evtype.healthpop.sum$sum.health, main="Health Problems(casuality)", ylab="persons")
barplot(storm.evtype.dmgtotal.sum$sum.dmg, main="Economic Damage", ylab="Dollars")
par(mfrow=c(1,1))
```

```{r total_damages_table, echo=TRUE}
storm.evtype.healthpop.sum$EVTYPE[which(storm.evtype.healthpop.sum$sum.health == max(storm.evtype.healthpop.sum$sum.health))]
storm.evtype.dmgtotal.sum$EVTYPE[which(storm.evtype.dmgtotal.sum$sum.dmg == max(storm.evtype.dmgtotal.sum$sum.dmg))]

head( storm.evtype.healthpop.sum[order(storm.evtype.healthpop.sum$sum.health, decreasing=TRUE),], 5 )
head( storm.evtype.dmgtotal.sum[order(storm.evtype.dmgtotal.sum$sum.dmg, decreasing=TRUE),], 5 )
```

```{r individual_effects, echo=TRUE}
# individual effects of fatality & injury / individual effects of product & crop #
storm.evtype.fatality.sum <- summarise(storm.evtype, sum.fatality = sum(FATALITIES, na.rm=TRUE))
storm.evtype.injuries.sum <- summarise(storm.evtype, sum.injuries = sum(INJURIES, na.rm=TRUE))
storm.evtype.propdmg.sum <- summarise(storm.evtype, sum.propdmg = sum(PROPDMG, na.rm=TRUE))
storm.evtype.cropdmg.sum <- summarise(storm.evtype, sum.cropdmg = sum(CROPDMG, na.rm=TRUE))
```

```{r fig.cap = "individual effects of fatality & injury"}
par(mfrow=c(1, 2))
barplot(storm.evtype.fatality.sum$sum.fatality, main="FATALITIES", ylab="persons")
barplot(storm.evtype.injuries.sum$sum.injuries, main="INJURIES")
par(mfrow=c(1,1))
```

```{r ind_health_damages_table, echo=TRUE}
storm.evtype.fatality.sum$EVTYPE[which(storm.evtype.fatality.sum$sum.fatality == max(storm.evtype.fatality.sum$sum.fatality))]
storm.evtype.injuries.sum$EVTYPE[which(storm.evtype.injuries.sum$sum.injuries == max(storm.evtype.injuries.sum$sum.injuries))]

head( storm.evtype.fatality.sum[order(storm.evtype.fatality.sum$sum.fatality, decreasing=TRUE),], 5 )
head( storm.evtype.injuries.sum[order(storm.evtype.injuries.sum$sum.injuries, decreasing=TRUE),], 5 )
```

```{r fig.cap = "individual effects of product & crop"}
par(mfrow=c(1, 2))
barplot(storm.evtype.propdmg.sum$sum.propdmg, main="PRODUCTS", ylab="Dollars")
barplot(storm.evtype.cropdmg.sum$sum.cropdmg, main="CROP")
par(mfrow=c(1,1))
```

```{r ind_economic_damages_table, echo=TRUE}
storm.evtype.propdmg.sum$EVTYPE[which(storm.evtype.propdmg.sum$sum.propdmg == max(storm.evtype.propdmg.sum$sum.propdmg))]
storm.evtype.cropdmg.sum$EVTYPE[which(storm.evtype.cropdmg.sum$sum.cropdmg == max(storm.evtype.cropdmg.sum$sum.cropdmg))]

head( storm.evtype.propdmg.sum[order(storm.evtype.propdmg.sum$sum.propdmg, decreasing=TRUE),], 5 )
head( storm.evtype.cropdmg.sum[order(storm.evtype.cropdmg.sum$sum.cropdmg, decreasing=TRUE),], 5 )
```
